%!TEX root = ../Thesis.tex
\chapter{System Design}
This section provides an overview of the system design for the development of a multi-agent system. The system design involves creating multiple instances of identical entities, simulating a real-world scenario where these entities would be physical robots connected to each other through some form of networking. To achieve this simulation, a microservices approach is employed, allowing for easy separation of agents, even on a single computer setup, and enabling the setup of constraints on computing power and memory usage.

The system design also incorporates the use of cloud and edge computing, with cloud computing being utilized for data gathering, computation, and visualization, and edge computing is utilized to model the behavior of agents. Communication and collaboration among the agents are facilitated through the implementation of mechanisms such as leader election, liveness checks, and local discovery. Additionally, this section will cover the implementation of data gathering and visualization and its integration into the overall system.

Python is chosen as the primary programming language for the implementation of this system. Python is a widely-used, high-level programming language that is known for its simplicity, readability, and flexibility \cite{python_docs}. Moreover, its extensive support for concurrency and parallelism allows for efficient and effective handling of large amounts of messages, which is crucial for the multi-agent system.
\section{Microservices}
\input{chapters/03_01_Microservices}

\section{Cloud Computing}
\input{chapters/03_02_Cloud_Computing}

\section{Local Computing}
\input{chapters/03_03_Edge_Computing}

\section{Communication Between Agents}
\input{chapters/03_04_Communication_Between_Agents}

\section{Leader Election}
\input{chapters/03_05_Leader_Election}

\section{Map Design}
\label{sec:03_06_Map_Design}
\input{chapters/03_06_Map_Design}

\section{Liveliness Algorithm}
\input{chapters/03_07_Liveness_algorithm}

\section{Visualization}
\label{sec:0308}
\input{chapters/03_08_Visualization}

\section{Multi tenancy}
\input{chapters/03_09_Multi_Tenancy}